An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
done with sec 6 up to a few proofs and writing

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\trimnonred}{\mathrm{trim}_{{\tt nonred}}}
\newcommand{\trimcover}{\mathrm{trim}_{\tt cover}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

@@

\jessie{Lemma X}
\begin{lemma}\label{lem:X}
  Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
  Then $L$ has a finite minimum representative set.
  Furthermore, letting $\Gamma = \prop{L}$, there exist finite sets
  $\V \subseteq \reals^\Y_+$ and
  $\Theta = \{\theta_v \subseteq \simplex \mid v\in\V\}$,
  both uniquely determined by $\risk{L}$ alone,
  such that
  \begin{enumerate}
  % \item There exists $\V = \V(\risk{L}) \subseteq \reals^\Y_+$, uniquely determined by $\risk{L}$ alone, such that $\V = L(\R^*)$.\label{item:X-V}
  \item A set $\R'\subseteq\R$ is representative if and only if $\V \subseteq L(\R')$.\label{item:X-rep-V}
  \item A set $\R'\subseteq\R$ is minimum representative if and only if $L(\R') = \V$.\label{item:X-min-V}
  \item A set $\R'\subseteq\R$ is representative if and only if $\Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.\label{item:X-rep-Theta}
  \item A set $\R'\subseteq\R$ is minimum representative if and only if $\{\Gamma_r \mid r \in \R'\} = \Theta$.\label{item:X-min-Theta}
  \item The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.\label{item:X-full-dim}
  \item For any $r \in \R$, there exists $\theta \in \Theta$ such that $\Gamma_r \subseteq \theta$.\label{item:X-redundant}
  \end{enumerate}
\end{lemma}

\raf{Make a corollary.  THus we'll focus on finite rep sets.}

\begin{proposition}\label{prop:SL-minimum}
  A minimizable loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite representive set.
  % Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  % \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
  A finite representative implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}.
  Lemma~\ref{lem:X} gives the converse.
\end{proof}

@@

To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} is equivalent to merely matching Bayes risks.
% For example, one can check that $\risk{\hinge} = 2\min\{p_1,p_2\} = 2\risk{\ellzo}$.
This useful fact will drive many of our results.

@@

\raf{Demote to corollary?}
\begin{proposition}\label{prop:embed-risk-poly}
  A minimizable loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and therefore $\risk{L}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Lemma~\ref{lem:X} gives a finite representative set $\Sc$, and $L$ embeds $L|_\Sc$ by Proposition~\ref{prop:representative-embeds-restriction}.
\end{proof}

\raf{Moved; reorganize}

From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.

Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.  As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-risk-poly} extends their result to the embedding setting.

Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.

\subsection{Minimum Representative Sets and Non-redundancy}
% commented out 19 Apr 21
% \raf{Some thoughts on this section:
% \begin{itemize}
% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%   \begin{itemize}
%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%   \end{itemize}
% \end{itemize}}
% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
% There are a few results that are well-explained by this:
% \begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimum representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
% \end{itemize}
% This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

\jessie{How do we want to think about finiteness here? Just assume it? }

In \S~\ref{sec:poly-loss-embed}, we discuss some implications of a representative set being minimum; here, we further investigate the relationship between minimum representative sets, non-redundancy of losses, and introduce what it means for an embedding to be tight.

@@

This motivates us to think about what it means to embed a non-redundant loss, and consider the implications this has for representative set.

\begin{definition}[Tight embedding]\label{def:tight-embedding}
  We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
\end{definition}

% \begin{definition}[Non-redundancy]\label{def:nonredundant}
%   A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
%   A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
% \end{definition}

% commented out 23 Apr 21
% \begin{proposition}\label{prop:min-rep-implies-trim}
%   Suppose $L$ elicits $\Gamma$.
%   If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
% \end{proposition}
% \begin{proof}
%   We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
%   For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
%   
%   \jessie{Implicit lemma about 3 ways to be redundant used here.}
%   We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
%   If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
%   If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
%   Therefore, $\Gamma_r \in \trim(\Gamma)$.
% \end{proof}
% 
% \begin{proposition}
%   Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
%   $L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
% \end{proposition}
% \begin{proof}
%   $\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
%   By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
%   Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
%   In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
%   
%   $\impliedby$
%   We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
%   In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
%   Therefore, $\R$ is not a minimum representative set.
% \end{proof}

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\U$ be a finite representative set for $L$.
  $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
\end{proposition}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  $\Rightarrow$  
  We show the contrapositive: suppose $L|_{\U}$ is redundant.
  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.

  \btw{Commenting out other statements with FDLS- Jessie 1 June 21}
%  $(b \implies c)$
%  If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
%  This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
%  Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy. \jessiet{Hand waving here}
%  Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.
%  
%  $(c \implies a)$
%  As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
%  Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
%  Therefore, $\R$ is minimum.

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Proposition~\ref{prop:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
  Since $\Gamma|_\U$ is non-redundant (Definition~\ref{def:nonredundant-prop}) by a corollary of the assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

\begin{corollary}\label{cor:tight-embed-min-rep}
  If $\R$ is a finite minimum representative set for $L$, then $L$ tightly embeds $L|_\R$. \raf{Changing def tight embed though...}
\end{corollary}
Tightly embedding the restricted loss seems to make embedding construction slightly easier.
While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier by a tight embedding.

We now present a concept called the $\trim$ of a loss (see Definition~\ref{def:trim-prop-nonred} for an analogous definition for properties in \S~\ref{app:embed-props}) which lets us focus on a unique set of loss vectors (resp., property values) induced by any minimum representative set.

\begin{proposition}\label{prop:trim-unique}
  Suppose $\R$ and $\R'$ are finite minimum representative sets for the loss $L$.
  Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}
  It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
  Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
  Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
  In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
  If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
  If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore either not a representative set or not minimum.
  Similarly, if the inequality were flipped, we would contradict either $\R$ being a representative set or minimum.
  Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

\begin{definition}[$\trimcover$]\label{def:trim-loss}
  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$. 
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.

  % commented out 06 May 21	
  %	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
  %	
  %	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
  %	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
  %	
  %	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
  %	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
  %	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
  %	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
  %	% Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.

  % commented out 03 May 21	
  %	Suppose $L(u) \in \trim(L)$.
  %	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
  %	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  %	
  %	Now, suppose $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  %	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
  %	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
  %	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
\end{proof}

It turns out that the $\trim$ of two losses being equal is equivalent to embedding, and additionally implies the existence of a tight embedding for a loss restricted to any minimum representative set.

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let the discrete loss $\ell$ be given.
  $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Moreover, when $\trimcover(L) = \trimcover(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$. \jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
\end{proposition}
Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
\begin{proof}[Sketch]
  $\implies$
  The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
  $\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
  By Proposition~\ref{prop:trim-unique}, we have
  \begin{equation*}
    \trimcover(L) = \trimcover(L|_{\varphi(\R)}) = \trimcover(\ell|_\R) = \trimcover(\ell)~.~
  \end{equation*}
  The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

>>>>

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\trimred}{\mathrm{trim}_{{\tt red}}}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\raf{Moved}
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.

@@

\jessie{Lemma X}
\begin{lemma}\label{lem:X}
  Let $L: \R \to \reals^\Y_+$ be a minimizable loss with a polyhedral Bayes risk $\risk L$.
  Then $L$ has a finite minimum representative set.
  Furthermore, letting $\Gamma = \prop{L}$, there exist finite sets
  $\V \subseteq \reals^\Y_+$ and
  $\Theta = \{\theta_v \subseteq \simplex \mid v\in\V\}$,
  both uniquely determined by $\risk{L}$ alone,
  such that
  \begin{enumerate}
  % \item There exists $\V = \V(\risk{L}) \subseteq \reals^\Y_+$, uniquely determined by $\risk{L}$ alone, such that $\V = L(\R^*)$.\label{item:X-V}
  \item A set $\R'\subseteq\R$ is representative if and only if $\V \subseteq L(\R')$.\label{item:X-rep-V}
  \item A set $\R'\subseteq\R$ is minimum representative if and only if $L(\R') = \V$.\label{item:X-min-V}
  \item A set $\R'\subseteq\R$ is representative if and only if $\Theta \subseteq \{\Gamma_r \mid r \in \R'\}$.\label{item:X-rep-Theta}
  \item A set $\R'\subseteq\R$ is minimum representative if and only if $\{\Gamma_r \mid r \in \R'\} = \Theta$.\label{item:X-min-Theta}
  \item Every representative set for $L$ contains a minimum representative set for $L$.\label{item:X-rep-contain-min}
  \item The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.\label{item:X-full-dim}
  \item For any $r \in \R$, there exists $\theta \in \Theta$ such that $\Gamma_r \subseteq \theta$.\label{item:X-redundant}
  \item $L$ tightly embeds $\ell:\R'\to\reals^\Y_+$ if and only if $\ell$ is injective and $\ell(\R') = \V$.
  \end{enumerate}
\end{lemma}

As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\R\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
As ``$L$ has a finite representative set'' is a more succinct condition than ``$L$ is minimizable and $\risk{L}$ is polyhedral'', we will use the former in the sequel.
(Recall that having a finite representative set already implies minimizability.)

@@

Lemma~\ref{lem:X} leads to another appealing equivalent condition to our embedding condition in Definition~\ref{def:loss-embed}: a surrogate embeds a discrete loss if and only if their Bayes risks match.

@@

Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss, but their result relies the Bayes risk of the surrogate being strictly concave.  As polyhedral functions are never strictly concave, Proposition~\ref{prop:embed-bayes-risk} extends their result to the embedding setting.

\subsection{Trimming a loss}

Central to the structural results in Lemma~\ref{lem:X} is the existence of a canonical set of loss vectors $\V$ which match the loss vectors of any minimum representative set.
This fact may seem surprising when one considers that losses may have many mimimum representative sets.
For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L(r)_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$.
Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.

Motivated by this observation, let us define the ``trim'' of a loss to be this unique set of loss vectors induced by any minimum representative set.

\begin{definition}[Trim]\label{def:trim-loss}
  Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trimcover(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

Using this notion of trimming a loss, we can again recast our embedding condition: a loss embeds another if and only if they have the same $\trim$.

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
  Then $L$ embeds a discrete loss $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
\end{proposition}
\begin{proof}
  As $L$ has a finite representative set, $\risk{L}$ is polyhedral, and Lemma~\ref{lem:X} applies; let $\V$ be the set of loss vectors uniquely determined by $\risk{L}$.
  If $L$ embeds $\ell$, then we have $\risk{L} = \risk{\ell}$ from Proposition~\ref{prop:embed-bayes-risks}.
  Thus, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.

  \raf{Fill in the rest...}
\end{proof}

\subsection{Minimum representative sets and non-redundancy}

The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general}\raft{TODO: see if there are other references we should include here.  Maybe Jessie you could search?}.
Intuitively, a loss is non-redundant if no report is weakly dominated by another report.

@@

From the structural result of Lemma~\ref{lem:X}, we can see that in fact these two notions are equivalent when $L$ has a polyhedral Bayes risk.
\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $L:\R\to\reals^\Y_+$ have a finite representative set $\R'$.
  Then $\R'$ is a minimum representative set for $L$ if and only if $L|_{\R'}$ is non-redundant.
\end{proposition}
\begin{proof}
  Let $\Gamma = \prop{L}$.
  Suppose first that $L|_{\R'}$ is redundant.
  Then there exist $r,r' \in \R'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Thus, for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore $\R' \setminus \{r\}$ still a representative set, so $\R'$ is not minimum.

  Now suppose $L|_{\R'}$ is non-redundant.
  As $\R'$ is a representative set, Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}) gives some minimum representative set $\Sc \subseteq \R'$.
  Suppose we had some $r \in \R' \setminus \Sc$.
  Now Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
  We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
\end{proof}

\begin{corollary}\label{cor:tight-embed-min-rep}
  Let loss $L:\R\to\reals^\Y_+$ and finite representative set $\Sc$ be given.
  Then $L$ tightly embeds $L|_\Sc$ if and only if $L|_\Sc$ is non-redundant.
\end{corollary}

\begin{corollary}\label{prop:trim-loss-condition}
  Let $L : \R \to \reals^\Y_+$ have a finite representative set.
  Then $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$. 
\end{corollary}
\begin{proof}
  \raf{Didn't get to this proof}

  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.
\end{proof}
